Research Notes

### 2020-06-19 notes/notes.tex
Wed June 17 notes
June 19 notes

                \item Near a phase transition, correlation length grows and changes become less likely to be accepted: need clusters. Clusters dont work far from the phase transition. This is manifested as a sequence of a few metropolis steps and a cluster step.
            \end{enumerate}
        \end{enumerate}
    \item Research plan
        \begin{enumerate}
            \item Start with 2D $\phi^4$

            \begin{enumerate}
                \item Set up lattice with sign flip for reflection
                \item Use Markov chain Monte Carlo to simulate.
                \item Measure, magnetization and suseptibility, Binder cumulant
            \end{enumerate}
            \item Transition to 3D, then maybe transition to C/C++.

            \item Implement the gradient flow

            \item move to 2-3d nonlinear sigma model.

            \item Motivation: the nonlinear sigma model works for QCD given the asymtotic freedom. We may also want to explore topology.

        \end{enumerate}
\nocite{*}
\bibliographystyle{plain}
\bibliography{notes}

@@

\end{document}

>>>>

            \item Near a phase transition, correlation length grows and changes become less likely to be accepted: need clusters. Clusters dont work far from the phase transition. This is manifested as a sequence of a few metropolis steps and a cluster step.
        \end{enumerate}
    \end{enumerate}
    \item Research plan
    \begin{enumerate}
        \item Start with 2D $\phi^4$
        \begin{enumerate}
            \item Set up lattice with sign flip for reflection
            \item Use Markov chain Monte Carlo to simulate.
            \item Measure, magnetization and suseptibility, Binder cumulant
        \end{enumerate}
        \item Transition to 3D, then maybe transition to C/C++.
        \item Implement the gradient flow
        \item move to 2-3d nonlinear sigma model. 
        \item Motivation: the nonlinear sigma model works for QCD given the asymtotic freedom. We may also want to explore topology.

    \end{enumerate}
\end{enumerate}

\section{Wednesday, June 17}
\begin{enumerate}
    \item Code tips:
    \begin{enumerate}
        \item Try Swendsen-Wang algorithm in addition to Wolff
        \item Print out time taken
        \item Optimize Hamiltonian
        \item Save every tenth measurement or store configurations to calculate path integral. Exclude thermaliztion (first 200)
        \item Write in terms of sweeps, not iterations
        \item Parallelize (look into checkerboard algorithm)
        \item Implement Binder cumulant and suseptibility
        \item Store every few states
        \item Look into multigrid algorithm

@@

    \item Reading on Monte Carlo Markov chain and cluster algorithms.
\end{enumerate}

\section{Friday, June 19}
    \begin{enumerate}
        \item Looking over code
        \begin{enumerate}
            \item Might be too slow, move to C/C++ eventually?
            \item Why is the energy increasing with metropolis algorithm?
            \item Shift to using action instead of Hamiltonian.
            \item Transition from Broken Phase, look at $\mu_0^2$ term.
            \item Profile code for possible optimizations.
        \end{enumerate}
    \end{enumerate}

\nocite{*}
\bibliographystyle{plain}
\bibliography{notes}
\end{document}
